---
title: "Will Mick Mulvaney be Replaced as Pres. Trump's Chief of Staff by 2020-01-01?"
output:
  html_document:
    highlight: pygments
    code_folding: hide
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This is my analysis for [This Question](https://www.gjopen.com/questions/1100-will-mick-mulvaney-cease-to-be-white-house-chief-of-staff-before-1-january-2020) on [Good Judgement Open](https://www.gjopen.com/).

## Chiefs of Staff

Wikipedia has already assembled [the list of Chiefs of Staff](https://en.wikipedia.org/wiki/White_House_Chief_of_Staff#List_of_White_House_chiefs_of_staff). All we needed to do was compile it into [a slightly cleaner format](https://docs.google.com/spreadsheets/d/e/2PACX-1vRlBabaJaIBmcqvF4QR4uF2megpcCpffX6doQbJaVWq8fMcfmW_iIdqs7iuYvi6LrtJkG5XjXnrybdg/pubhtml?gid=174141588&single=true).

```{r getData}
library(readr)
library(dplyr)
library(DT)
CoS <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vRlBabaJaIBmcqvF4QR4uF2megpcCpffX6doQbJaVWq8fMcfmW_iIdqs7iuYvi6LrtJkG5XjXnrybdg/pub?gid=174141588&single=true&output=csv')
CoS %>%
  select(Name, President, EnteredOffice, LeftOffice, TimeInOffice) %>%
  arrange(desc(EnteredOffice)) %>%
  datatable()
```

## Survival

To compute how long a Chief of Staff's tenure will be, let's fit a survival curve!

```{r survival}
library(survival)
library(survminer)
curve <- survfit(Surv(CoS$TimeInOffice) ~ 1)
plot(curve)
```

Now, since Mulvaney started on 2019-01-02, he'll need to be in his position 364 days to resolve the question as "No".

```{r continued}
window <- summary(curve, times=364)
window
```

So, the model suggests that he'll have a 364-day survival probability of `r window$surv`, and thus we predict that he'll be gone with probability `r 1-window$surv`

## Inside View

**(as of 2019-10-24)**

...suggests we should be so confident about his longevity:

* 2019-10-22 [Fox News says his job is in jeopardy](https://www.foxnews.com/media/mick-mulvaney-struggles-as-white-house-leaks-say-his-job-is-in-jeopardy)
* 2019-10-23 [President Trump Denies Rumors about replacement plans](https://www.politico.com/news/2019/10/23/trump-replace-chief-of-staff-mulvaney-055585)
* 2019-10-24 [Conservatives express support for
Mulvaney](https://www.politico.com/news/2019/10/24/mick-mulvaney-support-conservatives-056618)
